Scalar and Representative Observables for Polarimetric SAR Data

### 2013-10-02 paper_dev/article.tex
ready to submit to ian & nick

\usepackage{cite} %for citations
\usepackage{url}

@@

%How do others solve this problem?
%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
%  which apparently is multidimensional, complex and thus not very intuitive.
There has been a few scalar observables with accompanying statistical models proposal for POLSAR (TODO:CITE from section II),
  but none of them is able to provide meaningful scalar discrimination measures.
%  but none of them has led to scalar discrimination measures proposal.
As such no observable has been widely accepted as being highly representative of the multi-dimensional data,
  which severely limits their applicability in practical data processing applications.
From an alternative approach, there are also a few POLSAR discrimination measures proposed,
  but all of them are based on the likelihood ratio statistics.
This statistical test should be based on an exact and consistent statistical distribution
  but so far has only shown to be based on an asymptotic distribution.

>>>>

\usepackage{cite} %for citations
\renewcommand{\citedash}{--}
\usepackage{url}

@@

%How do others solve this problem?
%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
%  which apparently is multidimensional, complex and thus not very intuitive.
There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
  but none of them is able to provide meaningful scalar discrimination measures.
%  but none of them has led to scalar discrimination measures proposal.
As such no observable has been widely accepted as being highly representative of the multi-dimensional data,
  which severely limits their applicability in practical data processing applications.
From an alternative approach, there are also a few POLSAR discrimination measures proposed,
  but all of them are based on the likelihood ratio statistics.
This statistical test should be based on an exact and consistent statistical distribution
  but so far has only shown to be based on an asymptotic distribution.

### 2013-10-02 paper_dev/article_pp.tex
ready to submit to ian & nick

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
Similar to the SAR data, the POLSAR data is stochastic.
Moreover, it is multi-dimensional making it even harder to interpret.
Under this context, it is therefore important to establish a simple and intuitive understanding of the data
  and statistical models are undoubtedly crucial in understand the stochastic its nature.
While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.

@@

%(TODO: shorten the above 2 paragraphs. 

>>>>

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
Similar to the SAR data, the POLSAR data is stochastic.
Moreover, it is multi-dimensional making it even harder to interpret.
Under this context, it is therefore important to establish a simple and intuitive understanding of the data
  and statistical models are undoubtedly crucial in understand the stochastic its nature.
While several multidimensional models have been proposed for the POLSAR data,
  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.

@@
